TBD

### 2024-06-07 src/tex/ms.tex
[showyourwork] overleaf sync

% Main body with filler text
\section{Introduction}
\label{sec:intro}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/completeness.png}
    \caption{Caption}
    \label{fig:completeness}
    \script{completeness.py}
\end{figure}

@@

>>>>

% Main body with filler text
\section{Introduction}
\label{sec:intro}
The extent to which active galactic nuclei (AGN) impact galaxy formation is a major open question in astrophysics. It is clear that there is an interaction, from both observational and theoretical standpoints. Observations have revealed tight scaling relations between the mass of a super-massive black hole and its host galaxy \citep[see, e.g.][and references therein]{kormendy_coevolution_2013}, while cosmological simulations require some form of AGN feedback \citep{bower_breaking_2006,croton_many_2006} to be able to reproduce the observed galaxy population. Galaxies build up their stellar mass through star formation, while super-massive black holes are expected to provide either negative or positive feedback \hl{citations!} to either suppress or stimulate galaxy growth.

To understand the interplay between AGN activity and star formation (SF), it is necessary to measure both processes.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/simba_comparison.png}
    \caption{Caption}
    \label{fig:simba}
    \script{simba_comparison.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.98\textwidth]{figures/RLF_evolution_AGN.png}
    \caption{Caption}
    \label{fig:agn_evolution}
    \script{RLF_evolution.py}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.98\textwidth]{figures/RLF_evolution_SF.png}
    \caption{Caption}
    \label{fig:sf_evolution}
    \script{RLF_evolution.py}
\end{figure*}
